Manuscript Figures

### 2021-08-26 src/manuscript_figures.Rmd
drop unused functions

```{r}
plot_comp1 <- function(dt) {
  dt$method <- toupper(gsub("_factors", "", dt$method))
  comps <- lapply(setdiff(unique(dt$method), 'MAUI'), function(x) c('MAUI', x))
  ggboxplot(dt, 
          x = 'method', y = 'test_auc', color = 'method', 
          add = 'jitter', legend = 'none') + 
    stat_compare_means(method = 'wilcox.test', paired = T, 
                       method.args = list('alternative' = 'greater'), 
                     comparisons = comps) +
    labs(y = 'AUC') + theme(axis.text = element_text(size = 10))
}

plot_comp2 <- function(dt) {
  dt$method <- toupper(gsub("_factors", "", dt$method))
  dtc <- melt(dcast(dt, label ~ method, value.var = 'test_auc'), 
              id.vars = c('label', 'MAUI'))
  dtc$difference <- dtc$MAUI - dtc$value
  ggplot(dtc, 
         aes(x = MAUI, y = value)) + 
    geom_point() + geom_abline(slope = 1) + 
    facet_wrap(~ variable, nrow = 1) + 
    labs(y = 'AUC')
}

get_top_by_label <- function(dt, label.type, topN = 5) {
  do.call(rbind, lapply(split(dt, dt[,get(label.type)]), function(x) {head(x, topN)}))
}

@@

# combine adjusted survival curve plots into a single plot 
plots <- sapply(simplify = F, names(surv.stats), function(x) {   
  p <- surv.stats[[x]][['p']] 
  if(!is.null(p)) { 
    p + theme(axis.text.x = element_text(size = 8), 
              axis.text.y = element_text(size = 8), 
              axis.title.x = element_blank(), 
              axis.title.y = element_blank(), 
              legend.title = element_blank(),
              legend.position = c(0.5, 0.9),
              legend.text = element_text(size = 8), 
              legend.background = element_blank(), 
              legend.direction = 'vertical') 
    }
})
plots <- plots[!sapply(plots, is.null)]
p3 <- cowplot::plot_grid(plotlist = plots, nrow = 3, 
                   labels = sapply(strsplit(names(plots), '\\.'), function(x) x[1]), 
                   label_size = 8)

# print p3 to supplements 
supFig_count <- supFig_count + 1
SuppFigures[[supFig_count]] <- p3
fig.name <- paste0('SuppFigure', supFig_count, '.adjusted_survival_curves.pdf')
names(SuppFigures)[supFig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name), 
              plot = Fig, units = 'in', width = 8.27, height = 11.69)
SuppLegends[[supFig_count]] <- "Survival curves adjusted for tumor stage + age + gender based on a cutpoint of 
top survival-associated LF per cancer cohort."

>>>>

```{r}
get_top_by_label <- function(dt, label.type, topN = 5) {
  do.call(rbind, lapply(split(dt, dt[,get(label.type)]), function(x) {head(x, topN)}))
}

@@

# combine adjusted survival curve plots into a single plot 
plots <- sapply(simplify = F, names(surv.stats), function(x) {   
  p <- surv.stats[[x]][['p']] 
  if(!is.null(p)) { 
    p + theme(axis.text.x = element_text(size = 8), 
              axis.text.y = element_text(size = 8), 
              axis.title.x = element_blank(), 
              axis.title.y = element_blank(), 
              legend.title = element_blank(),
              legend.position = c(0.5, 0.9),
              legend.text = element_text(size = 8), 
              legend.background = element_blank(), 
              legend.direction = 'vertical') 
    }
})
plots <- plots[!sapply(plots, is.null)]
Fig <- cowplot::plot_grid(plotlist = plots, nrow = 6, 
                   labels = sapply(strsplit(names(plots), '\\.'), function(x) x[1]), 
                   label_size = 8)

# print p3 to supplements 
supFig_count <- supFig_count + 1
SuppFigures[[supFig_count]] <- Fig
fig.name <- paste0('SuppFigure', supFig_count, '.adjusted_survival_curves.pdf')
names(SuppFigures)[supFig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name), 
              plot = Fig, units = 'in', width = 8.27, height = 11.69)
SuppLegends[[supFig_count]] <- "Survival curves adjusted for tumor stage + age + gender based on a cutpoint of 
top survival-associated LF per cancer cohort."
```
